\documentclass[11pt,letterpaper,serif]{moderncv}       

% moderncv themes
\moderncvstyle{classic}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{grey}                             % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%onger than one page

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{amssymb}

% adjust the page margins
\usepackage[scale=0.85]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Prakhar}{Srivastav}
\address{6-19 Salmiya}{Kuwait, 13003}
\phone[mobile]{+965 9728 0350}
\email{prakhar1989@gmail.com}
\homepage{prakhar.me}

\begin{document}
\makecvtitle

%------- EDUCATION ---------%
\section{Education}
\cventry{2013-2011}{PGDM}{Indian Institute of Management, Calcutta}{India}{}{Ranked in top 10 percent of the batch - GPA: 7.12/9.00}
\cventry{2011--2007}{B.E.(Hons)}{Birla Institute of Technology and Science, Pilani}{Goa, India}{}{Computer Science Engineering - GPA: 7.71/10.00}

%------- EXPERIENCE ---------%
\section{Experience}
\subsection{\textbf{Professional}}

\cventry{2013--Present}{Xcite.com}{Ecommerce}{Alghanim Industries, Kuwait}{}{
\begin{itemize}
    %--- Developer ----%
    \item \textbf{Software Developer}
        \begin{itemize}
        \item Re-built the entire checkout functionality of the website to add the guest checkout feature on Angular.js as a single-page application
        \item Sole developer on the project to migrate the company's credit sales portal for customers from third-party provider to an in-house solution.
        \item Built strong \textbf{monitoring and alerting} tools to track uptime, availability and incident reporting.
    \end{itemize}
    %--- Business Analyst -----%
    \item \textbf{Business Analyst}
    \begin{itemize}
        \item Worked on improving website performance leading to decrease in page load time from \textbf{11 to 6sec}. 
        \item Improved existing \textbf{Insta-buy feature} and achieved cost-savings by replacing in-house card storage solution with \textbf{payment tokenization} from Cybersource.
        \item Led the project for migrating infrastructure from physical devices to a scalable \textbf{multi-tenant architecture} on cloud resulting in \textbf{cost-savings upto 50 percent}.
        \item Improved sales by scoping and leading the development of project to \textbf{sell digital products} (downloadable content) on Xcite.com. 
    \end{itemize}
    %---- Devops Engineer ----%
    \item \textbf{Devops Engineer}
        \begin{itemize}
            \item Responsible for managing infrastructure powering desktop, mobile web and mobile apps of one of the \textbf{highest traffic websites} in Kuwait
            \item Single-handedly responsible for all release, automated deployments, backups and developer environments across multiple channels
            \item Helped re-engineer the database architecture and led migration from failover replication to \textbf{multi master} for better flexibility and performance.
        \end{itemize}
\end{itemize}}

\subsection{\textbf{Open Source}}
\cventry{2013}{Developer}{getpostman.com}{Postman}{}{
\begin{itemize}
\item \textbf{Postman} Core developer on the Postman team. 
    \begin{itemize}
    \item Postman on Chrome is the most efficient way to test, develop and document APIs. 
    \item Highest rated developer productivity app on the Google Chrome store with more than \textbf{500,000} users amongst companies like Google, Khan Academy and Microsoft.
    \end{itemize}
\item \textbf{Newman} Built a command-line collection runner for making automated testing painless. 
    \begin{itemize}
    \item Allows users to integrate Postman collections with their Continous Integration system or run automated tests for their API through a cron job available as a node.js package on \href{https://www.npmjs.org/package/newman}{npm}. 
    \end{itemize}
\item \textbf{Postman Interceptor} Built a chrome extension for Postman 
\begin{itemize}
\item Allows chrome to send restricted headers and requests that use cookies directly to Postman.
\item The interceptor makes the process of testing APIs virtually painless as you can inspect live traffic directly in Postman. Available on \href{https://chrome.google.com/webstore/detail/postman-interceptor/aicmkgpgakddgnaphhhpliifpcfhicfo}{chrome web store.}
\end{itemize}
\end{itemize}
}

%------- INTERNSHIPS ---------%
\subsection{\textbf{Internships}}

\cventry{2012}{Marketing Intern}{Heinz Pvt. Limited}{Mumbai, India}{}{
\begin{itemize}
\item Drafted and assisted in implementing a promotion plan to drive sales of new SKUs of Complan.
\item Analyzed the entire marketing mix for new SKUs, gave suggestions to improve visibility, packaging and co-branding. Conducted extensive market research to understand consumer preferences.
\end{itemize}
}

\cventry{2011}{Developer Intern}{Travelocity, Sabre Holdings}{Bangalore, India}{}{
\begin{itemize}
\item Awarded pre-placement offer for performance and winning affiliate marketing competition during internship.
\item Successfully deployed an error-checking script to optimize user logging, worked on the mapper algorithm to increase its scalability.
\end{itemize}
}

%------- FREELANCE ---------%
\subsection{\textbf{Freelancer}}
\cventry{2013}{Full Stack Developer}{FMS Fiesta}{PHP, Yii, jQuery}{}{
\begin{itemize}
\item Designed and developed the website for one of the largest cultural festivals held by an Indian Business School - Faculty of Management Studies, Delhi
\end{itemize}}

\cventry{2012}{Rails Developer}{OhMyGreen}{Ruby on Rails, Facebook API}{}{
\begin{itemize}
\item Single-handedly ported a PHP Symfony app to Ruby on Rails for OhMyGreen (A silicon valley e-commerce startup by Stanford Alumni) featuring a complete registration and referral system.
\end{itemize}
}


%------- PROJECTS ---------%
\section{Projects}

\cvitem{Timelogger}{Timelogger is a Django backed full-featured time tracking application for entrprises to help employees track and manage their time spent on projects. \#django \#python}

\cvitem{Algorithms}{A collection of 30 essential data-structures and algorithms reimplemented in Python covering Dynamic Programming, Graph Algorithms and String algorithms. One of the \textbf{most popular} Algorithms library on Github. \#python}

\cvitem{Gettup}{Gettup is a simple command line utility which lets you share and upload files to the ge.tt sharing service quickly and easily. \#python}

%-- ADD ONE MORE PROJECT HERE %

\cvitem{Loops}{Loops is a web-based music player that allows users to listen to music directly from the web browser. It is Single Page Web App (SPA)  built without a JS MVC framework with flask as a minimal backend. \#javascript \#flask \#python}

\cvitem{More Projects}{Complete project list, open source work and repositories on \url{https://github.com/prakhar1989} and \url{http://prakhar.me/projects}}

%------- ONLINE COURSES --------%
\section{Online Courses}

    %---- COURSERA ---- %
    \subsection{\textbf{Coursera}}
    
        \cventry{2014}{Mining Massive DataSets}{Stanford}{Data Mining, Machine Learning}{}{
            \begin{itemize}
            \item A graduate-level CS course by Anand Rajaraman et al
            \end{itemize}
        }
        
        \cventry{2013}{Functional Programming in Scala}{EPFL}{Functional Programming}{}{
            \begin{itemize}
            \item Completed Course with 96.2\% marks and achieved distinction
            \item Learnt higher order functions, pattern matching and lazy evaluation
            \item Project: Built a code search engine in Scala for Stripe's Capture the Flag competition. Ranked in top 1000 worldwide.
            \end{itemize}
        }
        
        \cventry{2012}{Machine Learning}{Stanford}{Machine Learning}{}{
            \begin{itemize}
            \item Completed Course with 100\% marks and achieved distinction
            \item Learnt machine learning algorithms like regression, neural networks and support-vector machines
            \item Project: Built a movie recommendation engine using Collaborative Filtering in Python for Data Mining course in IIM Calcutta. Achieved highest grade and topped the course. 
            \end{itemize}
        }
        
        \cventry{2012}{Computing for Data Analytics}{John Hopkins}{Statistics}{}{
            \begin{itemize}
            \item Learnt programming in R, doing data analysis and creating data graphics in R.
            \end{itemize}
        }
    
    \subsection{\textbf{Udacity}}
        \cventry{2014}{Developing Android Apps}{Google}{Java}{}{
            \begin{itemize}
            \item Learnt UI development, connecting to the cloud and running services in Android Apps
            \item Project: Built an Android game - Colorphun and released it on the \href{https://play.google.com/store/apps/details?id=com.prakharme.prakharsriv.colorphun&hl=en}{Google Play Store}
            \end{itemize}
        }
        \cventry{2012}{Web Development}{Steve Huffman}{Python}{}{
            \begin{itemize}
            \item Learnt MVC design pattern, deployment on Google App Engine and scaling the application.
            \item Project: JokaStore: Built an e-commerce store from scratch for a venture as a part of Entrepreneurship course at IIM Calcutta. Project was hugely popular \& featured in India's leading daily - The Hindu.
            \end{itemize}
        }
        
%------- SKILLS ---------%
\section{Skills}
\cvitem{Languages}{Java, Python, Javascript, Ruby, HTML5/CSS3, Go, Scala, OCaml, Octave, C/C++}
\cvitem{Frameworks}{Django, Ruby on Rails, Node.js, Android, Flask, Sinatra, Backbone, jQuery, SASS, Less}

%---- RELEVANT COURSEWORK ------%
\section{Relevant Coursework}
    \cvitem{BITS}{Data Structures and Algorithms, Operating Systems, Theory of Computation, Database Systems, Advanced Computer Organization, Discrete Structures for Computer Science, Computer Programming I\&II, Object Oriented Programming.}
    
    \cvitem{IIM Calcutta}{Business Data Mining, Information Technology, Managing Information Systems, Managing New Ventures, IT and Business Innovation, Marketing for High-Tech and Innovation.}


%------ AWARDS AND HONORS ------%
\section{Awards and Honors} 
    \cvitem{2013}{Ranked in top 10\% of the batch at IIM Calcutta}
    \cvitem{2011}{Secured 99.80 \%ile in CAT 2011 amongst 300,000 students}
    \cvitem{2010}{Placed in top 5 at Sastra’10 – International Technical Festival of IIT Madras}
    \cvitem{2008}{Ranked 5th in ‘Mathematics Aptitude Test’ in a batch of over 600 students at BITS in ‘09}
    \cvitem{2007}{1st among 70 teams in Robotics Event at Quark '07 – National Technical Festival of BITS}
    \cvitem{2006}{Scholar Badge for 3 consecutive years(‘03 - ‘06) at Delhi Public School for academic excellence}
        
%----- EXTRA CURRICULAR ACTIVITIES -----%
\section{Extra-Curricular Activities}
    
    \subsection{\textbf{Positions of Responsibility}}  
        \cvitem{2012}{IT Head, Consulting Club - Developed the club's website with an inbuilt blogging platform}
        \cvitem{2011}{Member, IT Solutions Group - Developed the election portal, the course registration portal and research tracking portals for IIM Calcutta.}
        \cvitem{2010}{Core Member, Spree BITS - Designed merchandise and handled IT for the entire event.}
        \cvitem{2009}{Event Manager, Quark BITS - Organized the popular gaming event with a footfall of 75 teams.}
        
    \subsection{\textbf{Sports}}
        \cvitem{2007}{3rd Position in District Level Basketball Championship Sports}
        \cvitem{2006}{1st position in 100m Freestyle in Swimming Meet}


%------- INTERESTS ---------%
\section{Interests}
    \cvitem{Languages}{Love learning and trying out new programming languages (esp. functional)}
    \cvitem{Blogging}{I maintain a frequently updated tech blog at http://prakhar.me/}
    \cvitem{Featured on}{The Economic Times, The Hindu, The ChangeLog, PyCoder's Weekly}

\clearpage
\end{document}
